---
title: "Simulation Exercise"
author: "Evan Zhu"
date: "16/7/24"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this project I will investigate the exponential distribution in R and compare it with the Central Limit Theorem. I will investigate the distribution of averages of 40 exponentials with a thousand simulations.

```{r  results='hide',message=F}
library(dplyr)
library(ggplot2)
```

### Simulations

```{r simulations}
# set random seed
set.seed(170722)
lambda =0.2
simulations <- apply(matrix(rexp(1000*40,rate=lambda),1000),1,mean)
```

### 1. Show the sample mean and compare it to the theoretical mean of the distribution.

**Figure 1:**

```{r echo=FALSE}

hist(simulations,breaks=30,probability = T,main='Distribution of averages of samples',xlab='Simulation mean')
lines(density(simulations))
abline(v=1/lambda, col="red")

# theoretical density of the averages of samples
num <- seq(min(simulations), max(simulations), length=100)
density_theory <- dnorm(num, mean=1/lambda, sd=(1/lambda/sqrt(40)))
lines(num, density_theory, pch=15, col="blue", lty=2)

# add legend
legend('topright', c("simulation", "theoretical"), lty=c(1,2), col=c("black", "blue"))

```

As shown in the picture, the sample mean is similar to theoretical mean of the distribution. The sample mean is centered at `r mean(simulations)`, close to `r 1/lambda`.

###  2. Show how variable it is and compare it to the theoretical variance of the distribution

```{r results= 'hide'}

var(simulations)
(1/lambda)^2/40

```
The standard deviation of simulation is `r sd(simulations)`, and variance of simulation is `r var(simulations)`. The variance of simulations is similar to `r (1/lambda)^2/40`. And displayed in Figure 1, the vairance is close. 

### 3. Show that the distribution is approximately normal
**Figure 2:**
```{r}

qqnorm(simulations); qqline(simulations)

```

As shown in Figure 1 and Figure 2, the distribution is approximately normal. 


